Insert the article title here

### 2020-07-24 tex/results.tex
Add more context into ellis replication

There are two results from this paper that we aim to replicate, and one of them is a comparison
against experimental results which will lead to a validation.

The first result we show is a replication of a result presented in their supplementary 
material FigureS4 {\color{red}(note sure how to cite this, maybe a link)}. We aimed to replicate the 
black curve since the simulation setup is possible to replicate using PyGBe. For each aspect ratio (AR) 
value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
800-1000 $cm^{-1}$, we identify the the lower frequency mode ($E_{100}$ in Ellis paper)  that is not a 
longitudinal mode. We identify the Longitudinal modes by comparing normal vs 22 deg incidence runs. These
modes due to its nature do not show up in the normal incidence runs. Then, on the 22 deg incidence 
computations we choose the lower wave number mode that it's not a longitudinal mode. The simulations were 
performed for the Long Edge orientation, meaning that the electric field is polarized along the long edge 
of the pillar that is not the height.

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_22_vs_norm.pdf} 
    \caption{ Extinction cross section across wave number for SiC pillars of multiple Aspect ratios. 
             (H=950 nm, W=400nm, L=400-2800 (AR=1-7))
            Normalized by maximum extinction cross section as a function of wave number,
            for a pillar orientation such that the electric field is parallel polarized 
            (I HAVE TO EXPLAIN THIS BETTER, IT ALIGNS WITH THE LENGTH OF THE PILLAR). 
            We present the results for normal incidence and 22 degrees incidence, 
            for different aspect ratios (AR)}
    \label{fig:AR_22_vs_norm}
 \end{figure}

\begin{table}
    \begin{center}
      \caption{Wavelength at which peaks happen for different aspect ratios, for runs where the electric
      field is parallel to the length (L) of the pillar. We have normal incidence and 22 degrees.}
      \label{tab:table1}
      \begin{tabular}{c c c c c c c c}
        \textbf{AR} \\
        \hline
        \multirow{2}{*}{1} & $\perp$ & \textbf{917.73} & 934.092 & 949.604 & 957.325 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & 883.926 & \textbf{917.73} & 935.052 & 949.604 & 957.325 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{2} & $\perp$ & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & 896.517 & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{3} & $\perp$ & \textbf{888.793} & 922.552 & 931.223 & 948.613 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{888.793} & 899.418 & 922.552 & 931.223 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{4} & $\perp$ & \textbf{876.186} & 929.32 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{876.186} & 901.281 & 921.618 & 929.32 & 945.745 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{5} & $\perp$ & \textbf{865.576} & 926.395 & 945.745 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{865.576} & 901.281 & 921.618 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{6} & $\perp$ &  \textbf{856.904} & 914.793 & 923.489 & 929.32 & 946.639 & 958.242\\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{856.904} & 901.281 & 920.6 & 958.242\\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{7} & $\perp$ &  \textbf{850.134} & 910.963 & 921.618 & 928.372 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{850.134} & 901.281 & 910.963 & 920.6 & 958.242\\ % <-- Content of first column omitted.
        \hline

      \end{tabular}
    \end{center}
  \end{table}

In other words, we choose the lower mode (lower wavenumber) from the normal 
incidence cases.

Our simulations differ on the method and we do not have a substrate included. The black curve on 
Ellis et al \cite{ellis2016} represents the resonance positions for the $E_{100}$ mode for the different 
aspect ratios when the pillar are separated by a 5000 nm gap. The simulations performed with \pygbe 
consist of one isolated pillar.

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
    \caption{Replication of figure S4 of supplementary material of Ellis 2016}
    \label{fig:rep_FS4_ellis}
 \end{figure}

 If we calculate de relative percentage error for each of these points we get:

 \begin{table}
    \centering
    \caption{\label{table:err_AR} Percentage error for different aspect ratios.} 
    \begin{tabular}{c c}
    \hline%\toprule
    ARR & \% error \\
    \hline%\midrule
     $1$ & $0.95$ \\
     $2$ & $0.67$ \\
     $3$ & $0.35$ \\
     $4$ & $0.16$ \\
     $5$ & $0.72$ \\
     $6$ & $1.20$ \\
     $7$ & $1.59$ \\
    \hline%\bottomrule
    \end{tabular}
\end{table}

>>>>

 %%% Ellis work summary %%%%
The work of Ellis and coworkers \cite{ellis2016} study the aspect-ratio evolution of high-order
resonant modes in localized surface phonon-polariton nanostructures. They study the
excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
polarized reflectance measurements on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
width ($W=400$ nm) and varied length ($L=400-4800$ nm) and therefore an aspect ratio
($AR=L/W=1-12$). These pillars are patterned on a squared grid with a pitch $P=L+500$ nm
to reduce coupling. In their simulations and experiments they excite the localized SPhP
resonances, they perform polarized reflectance measurements with the incident polarization 
oriented parallel or perpendicular to the long axis of the pillars.  
 %%% Ellis work summary %%%%

We aim to replicate the computational result presented in Figure S4 of their supplementary 
material (NOT SURE HOW TO CITE THIS) that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We first attempted to replicate this result since they have simulations with the gap between pillars 
is 5000 nm, and this cause negligible coupling. This result is suitable to compare with 
what we can model using \pygbe.

\textit{methods}
In Ellis et al simulations they solve full Maxwell equations via the RF package of the finite
element method software COMSOL. To represent the array of pillars and their interactions, they use
periodic boundary conditions of one pillar over a portion of substrate. They present the reflectance 
as a function of the wave number. As we mentioned before, we use the boundary element method in 
the quasistatic approximation, which is suitable in these case since Ellis pillar's size is small 
compared to the wavelength involved in the simulations (800-1000 cm$^-1$). We measure extinction cross 
section, which will express as peaks instead of inverted peaks (as in reflection) since you see maximum
extinction when there is minimum reflection. The intensity of the peaks is not comparable, but we are 
looking to match the wave number at which these events happen.

\textit{mesh}
For the case of aspect ratio AR=4 we count with a triangular surface mesh provided by the authors of 
Ellis et al. Which is a non-structured mesh of approximately 4 thousand elements. To produce the remaining 
meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
uniform mesh, we needed to double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
I'M NOT SURE IF WE WANT TO PUT THEM, SINCE WE DON'T HAVE SPACE).
To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
replication of figure 2a and the validation result we used the mesh provided by the authors of Ellis et al.

\textit{dielectric data}
The dielectric data for the simulations, was given by the authors of the paper via a private communication.

To be able to replicate this results, we need to identify the lower frequency mode for each of
the aspect ratios in our computations. For each aspect ratio (AR) 
value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
800-1000 $cm^{-1}$. We identify the lower frequency mode ($E^{\parallel}_{100}$ in Ellis paper)  that is not a 
longitudinal mode (mode related to the hight of the pillar, only visible when the incidence of the 
electric field is not normal). We can identify the longitudinal modes by comparing normal vs 22 degrees 
angle of incidence runs. As we mentioned the longitudinal modes, due to its nature, do not appear when we 
have the normal incidence . Then, on the 22 degree incidence computations we choose the lower wave number mode
that it's not a longitudinal mode.

Figure \ref{fig:AR_22_vs_norm} show the results of the extinction cross section of a SiC pillar of fixed
height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400-2800$ nm). The simulations where performed 
performed for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
when having normal incidence. (I SHOULD PROBABLY MAKE A DIAGRAM OF THIS)

In Figure \ref{fig:AR_22_vs_norm} and Table \ref{tab:ar_peaks} we show the resonance peaks and
their corresponding wavelengths. In the table we mark in bold the peaks which correspond to 
the $E^{\parallel}_{100}$ mode.

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_22_vs_norm.pdf} 
    \caption{Extinction cross section across wave number for SiC pillars of multiple aspect ratios,  
             (H=950 nm, W=400nm, L=400-2800 nm (AR=1-7)), where we have normal incidence and a 
             22 degrees incidence.
            }
    \label{fig:AR_22_vs_norm}
 \end{figure}

\begin{table}
    \begin{center}
      \caption{Wavelength at which peaks happen for different aspect ratios, for runs where the electric
      field is parallel to the length (L) of the pillar. We have normal incidence and 22 degrees.}
      \label{tab:ar_peaks}
      \begin{tabular}{c c c c c c c c}
        \textbf{AR} \\
        \hline
        \multirow{2}{*}{1} & $\perp$ & \textbf{917.73} & 934.092 & 949.604 & 957.325 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & 883.926 & \textbf{917.73} & 935.052 & 949.604 & 957.325 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{2} & $\perp$ & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & 896.517 & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{3} & $\perp$ & \textbf{888.793} & 922.552 & 931.223 & 948.613 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{888.793} & 899.418 & 922.552 & 931.223 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{4} & $\perp$ & \textbf{876.186} & 929.32 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{876.186} & 901.281 & 921.618 & 929.32 & 945.745 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{5} & $\perp$ & \textbf{865.576} & 926.395 & 945.745 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{865.576} & 901.281 & 921.618 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{6} & $\perp$ &  \textbf{856.904} & 914.793 & 923.489 & 929.32 & 946.639 & 958.242\\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{856.904} & 901.281 & 920.6 & 958.242\\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{7} & $\perp$ &  \textbf{850.134} & 910.963 & 921.618 & 928.372 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{850.134} & 901.281 & 910.963 & 920.6 & 958.242\\ % <-- Content of first column omitted.
        \hline
      \end{tabular}
    \end{center}
  \end{table}

Once we identify the proper modes, we proceed to the replication of Figure S4 on the 
supplementary material of Ellis et al work. It is worth mentioning that we limit ourselves to
the replication of the black curve in their plot, since in this case the pillars are separated 
by 5000 nm which means the coupling effects are negligible. Figure \ref{fig:rep_FS4_ellis} shows
the results from  Ellis et al (digitized using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all
the cases

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
    \caption{Replication of figure S4 of supplementary material of Ellis 2016. Wave
    number at which happens the $E^{\parallel}_{100}$ mode for different aspect ratios.}
    \label{fig:rep_FS4_ellis}
 \end{figure}

 \begin{table}
    \centering
    \label{tab:err_AR}
    \caption{Percentage error for different aspect ratios.} 
    \begin{tabular}{c c}
    \hline%\toprule
    ARR & \% error \\
    \hline%\midrule
     $1$ & $0.95$ \\
     $2$ & $0.67$ \\
     $3$ & $0.35$ \\
     $4$ & $0.16$ \\
     $5$ & $0.72$ \\
     $6$ & $1.20$ \\
     $7$ & $1.59$ \\
    \hline%\bottomrule
    \end{tabular}
\end{table}
